Practicing with the data

### 2017-07-12 practice.Rmd
more variable exploration

#26 observations in out dataframe have negative time to event variable
length(which(out$time_until_answer < 0))
library(dplyr)
out %>% 
  filter(time_until_answer < 0) %>%
  select(post_date, first_answer_date, answered)
```

### Practicing with stringr 
```{r}
library(stringr)
library(rebus)

#variable indicating if title contains questionmark 
out$contain_questionmark <- str_detect(out$title, pattern = QUESTION)

#practicing with product categorization
phones <- regex("phone", ignore_case = TRUE)
out$product_type[str_detect(out$device, pattern = phones)] <- "Phone"
```

### Practicing with dplyr
```{r}
library(stringr)
library(dplyr)

#using only observations in English
out_english <- out %>% 
                tbl_df() %>% 
                filter(langid == "en")

@@

#view average time until answered grouped by whether or not question contains "?", for each category
#seems like for a lot of categories, questions with question marks get answered faster
out_english$contain_questionmark <- str_detect(out_english$title, pattern = QUESTION)
out_english %>%
  group_by(category, contain_questionmark) %>%
  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n()) %>%
  arrange(category, avg_time)

#looking at average time until answered for intervals of title length
#creating title length intervals
title_length <- str_length(out_english$title)
out_english$title_length_intervals <- cut(title_length, breaks = 8)
#don't really see anything interesting here 
out_english %>%
  group_by(title_length_intervals) %>%
  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n())

@@

### practicing with ggplot
```{r}
library(ggplot2)
library(stringr)

#using only observations with a positive time_until_answer value (26 observations have negative time until answer values)
out1_positive <- out_english %>% filter(time_until_answer > 0)

#histogram of time_until_answer
ggplot(out1_positive, aes(x = time_until_answer)) + 
  geom_histogram(bins = 10)

#plot of number of tags and time_until_answer
ggplot(out1_positive, aes(x = factor(n_tags), y = time_until_answer)) + 
  geom_point(position = "jitter")

#plot with title length 
out1_positive$title_length <- str_length(out1_positive$title)

ggplot(out1_positive, aes(x = title_length, y = time_until_answer)) + 
  geom_point()

#looking at only data for phones category 
phones_only <- out1_positive %>% filter(category == "Phone")
ggplot(phones_only, aes(x = title_length, y = time_until_answer)) + 
  geom_point(size = 3, alpha = 0.5)
```

>>>>

#subsetting to include only questions in english
library(dplyr)
out_english <- out %>% 
                tbl_df() %>% 
                filter(langid == "en")
```

### exploring time to event variable
```{r}
summary(out_english$time_until_answer)

library(ggplot2)

#defining tick marks for x-axis
min <- min(out_english$time_until_answer)
max <- max(out_english$time_until_answer)

require(scales)
ggplot(out_english, aes(x = time_until_answer)) + 
  geom_histogram(bins = 10) + 
  scale_x_continuous(labels = comma, breaks = seq(min, max, by = (max-min)/10)) + 
  theme(axis.text.x = element_text(angle=90, hjust=1))

#zoomed in histogram of responses
ggplot(out1, aes(x = time_until_answer)) + 
  geom_histogram() + 
  scale_x_continuous(limits = c(20, 30000))

boxplot(out_english$time_until_answer)
bstats <- boxplot.stats(out_english$time_until_answer)
bstats
#797 questions lie outside of the whiskers
```

### exploring the categories 
```{r}
table(out_english$category)

@@

#looking at median time_until_answer since data is skewed right
out_english%>%
  group_by(category) %>%
  summarise(median_time = median(time_until_answer, na.rm = TRUE), num = n()) %>%
  arrange(median_time)

#looking at time_until_answer distributions according to Mac, PC, Phone, showing whether or not the question contains a question mark
ggplot(subset(out_english, category %in% c("Mac", "PC", "Phone")), aes(x = time_until_answer, fill = as.factor(contain_questionmark))) +
  geom_histogram(bins = 10) + 
  facet_grid(.~category)

#looking at only data for phones category (nothing interesting here)
phones_only <- out_english %>% filter(category == "Phone")
ggplot(phones_only, aes(x = title_length, y = time_until_answer)) + 
  geom_point(size = 3, alpha = 0.5)
```

### investigating whether a question mark is present or not
```{r}
library(stringr)
library(rebus)

#variable indicating if title contains questionmark 
out_english$contain_questionmark <- str_detect(out_english$title, pattern = QUESTION)
sum(out_english$contain_questionmark)

#view average time_until_answered grouped by whether or not question contains "?", for each category
#seems like for a majority of the categories, questions with question marks get answered faster
out_english %>%
  group_by(category, contain_questionmark) %>%
  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), median =
              median(time_until_answer, na.rm = TRUE), num = n()) %>%
  arrange(category, avg_time)

#calculating proportion of questions that contain a question mark that were answered
q <- out_english %>%
        filter(contain_questionmark == T)
sum(q$answered)/nrow(q)

#proportion of questions that contain ? for each category
prop.table(table(out_english$category, out_english$contain_questionmark), 1)
```

### exploring title length
```{r}
#creating title_length variable
out_english$title_length <- str_length(out_english$title)
hist(out_english$title_length)
summary(out_english$title_length)

#viewing average/median title length for each category and comparing it to average time until answer
out_english %>%
  group_by(category) %>%
  summarise(avg_length = mean(title_length), median_length = median(title_length), avg_time = mean(time_until_answer), n = n()) %>%
  arrange(avg_length)

#creating title length intervals
out_english$title_length_intervals <- cut(out_english$title_length, breaks = 8)
#don't really see anything interesting here 
out_english %>%
  group_by(title_length_intervals) %>%
  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n())

#plot with title length 
#randomly subset half of the data set to make easier to read
#don't see any association 
ggplot(sample_frac(out_english, size = 0.50, replace = FALSE), aes(x = title_length, y = time_until_answer)) + 
  geom_point()
```

### exploring text length
```{r}
out_english$text_length <- str_length(out_english$text)
hist(out_english$text_length, xlim = c(0,3000))
summary(out_english$text_length)

#examining avg/median text length and comparing it to avg time_until_answer for each category
out_english %>%
  group_by(category) %>%
  summarise(avg = mean(text_length), median = median(text_length), avg_time = mean(time_until_answer), n = n()) %>%
  arrange(avg_time)
```

### exploring device length (find another way to classify how detailed device is)
*observation 7548 has a 136 character string for it's device
```{r}
out_english$device_length <- str_length(out_english$device)
hist(out_english$device_length)
summary(out_english$device_length)

#don't see anything interesting here
out_english %>% 
  group_by(category) %>%
  summarise(avg = mean(device_length), median = median(device_length), avg_time = mean(time_until_answer), n = n()) %>%
  arrange(avg_time)

@@

### examining the number of tags for a question
```{r}
summary(out_english$n_tags)

#proportion of questions that don't have any tags
sum(out_english$n_tags == 0)/nrow(out_english)
table(out_english$n_tags)

#viewing average time_until_answer grouped by number of tags and category
out_english %>%
  group_by(category, as.factor(n_tags)) %>%
  summarise(avg_time = mean(time_until_answer), n = n()) %>%
  arrange(category)

#plot of number of tags and time_until_answer (nothing interesting here)
ggplot(out_english, aes(x = factor(n_tags), y = time_until_answer)) + 
  geom_point(position = "jitter")
```

### number of pictures included 
```{r}
summary(out_english$n_images)
hist(out_english$n_images)
table(out_english$n_images)

#proportion of questions that include any images
sum(out_english$n_images != 0)/nrow(out_english)

#looking at mean time_until_answer grouped by n_images
out_english %>% 
  group_by(as.factor(n_images)) %>%
  summarise(avg_time = mean(time_until_answer), n = n()) %>%
  arrange(avg_time)

#looking at mean time_until_answer grouped by categories and n_images
out_english %>%
  group_by(category, as.factor(n_images)) %>%
  summarise(avg_time = mean(time_until_answer), median = median(time_until_answer), n = n()) %>%
  arrange(category, avg_time)
```
